---
title: "Lab 00 - Hello IDS!"
author: "Finlay D. Webb"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Cameron Fisher", "Harry English", "Tom Cummings", 
           "Fin McLachlan", "Evan Huwe"),
  github_username = c("cameronfisher05", "Harryenglish", "tom-rex", 
                      "finmc3", "evanh05"), 
  colour = c("blue", "blue", "red", 
             "blue", "blue"),
  hobby = c("golf", "boxing", "data science", 
            "chasing people", "cricket"),
  favourite_number = c(7, 6.02, 2.7, 1, 6.6)
  )

team_data
```

### Exercise 18

We now work on visualising our data.  .

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


A bar chart with our favourite numbers visualised on the y-axis.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Names of table", 
          y = "Favourite number",
          title = "A graph to show data from table 9")
```

Lab, appears to be the function that puts labels on a plot or graph.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

The hobbies are too different from each other, it would be better to group hobbies into sports and other categories, that way you could see just 4 parts to the bar chart, rather than 100+, for the 100+ people in the data set.
